Title

### 2018-09-01 thesis/paper/paper.tex
Minor improvements

To improve the data quality, to help editors avoid common mistakes and to clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are, however, not firm rules and exceptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. that only certain values are allowed, or more complex requirements on connected parts of the data graph, e.g. that the value of a statement with this property should have certain statements. In Table \ref{tab_property_constraints} you can find the existing property constraints. Afterwards the constraints will be explained in detail and a basic approach for their modelling given. For constraint that cannot be modelled, reasoning for this assessment is included.

@@

Table \ref{tab_property_constraints} shows all constraints that are used as of September 2018. It is roughly sorted by how difficult it is to model the given constraint using logical rules, based on the required expressive features and pre-processing. These required features are conditions that cannot natively be expressed in datalog and would require some kind of pre-processing of the dataset. Four constraints do not need any pre-processing except for loading the data into datalog as ground rules. Six can be solved if constant inequality is defined. This can be easily solved with brute force but will be improved in section \ref{sec_inequality}. A further seven require negation of a specific fact which can be achieved with reasonable effort. The last ten \todo{maybe type can be done in some way} are not deemed translatable because they require a feature that cannot be reasonably emulated in datalog. The feature mostly needed is a general form of negation that would allow to test for the non-existence of a derived fact. Other features needed for these constraints are regular expressions, which could theoretically be translated but would require large amounts of pre-processing, value comparison, and finally web requests to test if a link is valid.

>>>>

To improve the data quality, to help editors avoid common mistakes and to clarify the usage of properties, Wikidata allows constraints to be defined on properties. They are, however, not firm rules and exceptions can and should be made if necessary. A property constraint says something about the way a property may or may not be used. This can mean simple restrictions on the statement a property is part of, e.g. that only certain values are allowed, or more complex requirements on connected parts of the data, e.g. that the value of a statement with this property should have certain statements. In Table \ref{tab_property_constraints} you can find the existing property constraints as of September 2018. Afterwards the constraints will be explained in detail and their modelling given. For constraint that cannot be modelled, reasoning for this assessment is included.

@@

Table \ref{tab_property_constraints} shows all constraints that are used as of September 2018. It is roughly sorted by how difficult it is to model the given constraint using logical rules, based on the required expressive features and pre-processing. These required features are conditions that cannot natively be expressed in datalog and would require some kind of pre-processing of the dataset. Four constraints do not need any pre-processing except for loading the data into datalog as ground rules. Six can be solved if constant inequality is defined. This can be easily solved with brute force but will be improved in section \ref{sec_inequality}. A further seven require negation of a specific fact which can be achieved with reasonable effort. The last ten are not deemed translatable because they require a feature that cannot be reasonably emulated in datalog. The feature mostly needed is a general form of negation that would allow to test for the non-existence of a derived fact. Other features needed for these constraints are regular expressions, which could theoretically be translated but would require large amounts of pre-processing, value comparison, and finally web requests to test if a link is valid.
